\section{Related Work}

\subsection{Deep Reinforcement Learning \& Non-Stationary Environments}
Deep Reinforcement Learning (DRL) typically assumes that the underlying Markov Decision Process (MDP) remains stationary throughout training and deployment. When an environment transitions—such as shifting physics in robotics \cite{zhao2020sim} or varying task parameters—traditional methods like Deep Q-Networks (DQN) \cite{mnih2015human} suffer from catastrophic forgetting. Modifying weights to solve the newly presented environment invariably overwrites the synaptic memories associated with the previous tasks, leading to an inability to seamlessly generalize backwards once the environment shifts again.

\subsection{Evolutionary Reinforcement Learning (ERL)}
To bypass the limitations of single-agent gradient descent, Evolutionary Reinforcement Learning (ERL) merges population-based Evolutionary Algorithms (EA) with DRL gradient optimization \cite{khadka2018evolutionary}. ERL maintains a population of neural networks that share experiences and heavily map the parameter space, largely protecting the architecture from local minima. However, standard ERL often treats the population simply as a wide exploration mechanism for a single overarching actor. In contrast, ENA explicitly relies on the population as an ensemble of independent behavioral memories that can individually adapt to separate non-stationary sub-domains.

\subsection{Quality-Diversity and MAP-Elites}
Our methodology mathematically aligns with the emerging field of Quality-Diversity (QD) algorithms. Unlike traditional EAs that strive to discover a singular global optimum, QD algorithms like MAP-Elites \cite{mouret2015illuminating} explicitly seek to create an archive of diverse, high-performing behaviors. The work most parallel to our own is \textit{Intelligent Trial and Error} by Cully et al. \cite{cully2015robots}, which demonstrated that a robot with a broken leg could adapt in less than two minutes by searching a pre-computed MAP-Elites repertoire of alternative gaits. The Evolutionary Neuroplastic Agent (ENA) natively internalizes this paradigm; instead of depending on offline pre-computation, ENA autonomously regulates its diverse ``Hall of Fame" archive entirely online driven iteratively by its mathematical abstractions of Trust and Plasticity.
