Traditional Reinforcement Learning (RL) agents often struggle to adapt rapidly in non-stationary environments, suffering catastrophic forgetting when facing sudden physical shifts. Drawing inspiration from biological meta-learning and evolutionary diversity, this preliminary study introduces the Evolutionary Neuroplastic Agent (ENA). The ENA dynamically maintains an active population of multiple lightweight neural network policies (a ``pool of specialists") instead of a monolithic model. By continuously evaluating each specialist iteratively through defined \emph{Trust} and \emph{Plasticity} heuristics, the ENA autonomously triggers localized evolutionary search algorithms and substitutes specialists during environmental changes. We empirically evaluate two mechanisms for governing these shifts: a Quadratic Ratio formulation and a normalized Fuzzy-logic heuristic model. Evaluating this framework in a continuously shifting 1D CartPole domain transitioning across sequential gravities (Earth, Mars, Jupiter), we execute an online meta-learning testing protocol comparing frozen neural behaviors sequentially across those bodies tracking into a hidden fourth phase (Neptune). We demonstrate that the Fuzzy-logic framework manages inter-environment stability gaps smoothly. However, the study identifies critical limitations: the ENA exhibits massive standard-deviation dependencies on initial population states, confirming that robust adaptation within tightly constrained genetic boundaries remains highly vulnerable to initial parameter clustering. Our findings position the ENA as a promising proof-of-concept for dynamic Quality-Diversity adaptation, warranting further benchmarking against standard deep RL alternatives in complex domains.
